---
title: "Session 3 Tasks"
author: "Andreas Angourakis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

```{r}


# Combining the vectors into a data frame
stone_tools_data <- data.frame(
  inventory_number = c("LN15", "LN17", "LN18", "LN21", "LN23", "LN24"),
  blength = c(18, 14, 21, 14, 17, 16),
  breadth = c(9, 7, 10, 7, 8, 8),
  thickness = c(3, 2, 3, 3, 3, 2),
  material_type = c("chert", "chert", "obsidian", "chert", "obsidian", "obsidian"),
  material_provenance = c("local", "local", "local", "non-local", "local", "non-local")
)

stone_tools_data

# Display the data frame
knitr::kable(stone_tools_data)
```

Save it as a CSV file (stored in a “data” subdirectory) and load it back as a new R object (e.g. “stone_tools_data2”).

```{r}
# Base R
write.csv(stone_tools_data, "data/stone_tools_data.csv")
```

Compare.

```{r}
stone_tools_data2 <- read.csv("data/stone_tools_data.csv")[,-1]
```

Create a plot showing the counts of objects made of chert and obsidian.

```{r}
# Base R
stone_tools_data_table_type <- table(stone_tools_data$material_type)
png("plots/session3_barplot_barplot.png")
barplot(stone_tools_data_table_type,
        main = "Bar Plot of count ...",
        xlab = "Material type ",
        )

dev.off()
```

Create a new variable (“type_and_provenance”) that combines type and provenance and create a plot showing the counts in each category. Save it as a PNG file in “plots” subdirectory.

```{r}
stone_tools_data$type_and_provenance <- paste(stone_tools_data$material_type, stone_tools_data$material_provenance, sep = " and ")

```

Create a single figure displaying the variable distribution of the three dimensions measured. Save it as both a PNG and a SVG file in “plots” subdirectory.

```{r}
# 20241129
stone_tools_data_table_type_and_provenance <- table(stone_tools_data$type_and_provenance)
png("plots/session3_barplot_type_and_provenance.png")
#svg("plots/session3_barplot_type_and_provenance.svg")
barplot(stone_tools_data_table_type_and_provenance,
        main = "Bar Plot of count of artifacts by material type and provenance",
        xlab = "Material type and provenance",
        )

#dev.off()
```

Create a single figure displaying the variable distribution of the three dimensions measured. Save it as both a PNG and a SVG file in “plots” subdirectory.

```{r}
png("plots/session3_barplot_type_and_provenance_ggplot2.png", width = 700)
svg("plots/session3_barplot_type_and_provenance_ggplot2.svg")
ggplot(stone_tools_data, aes(x = type_and_provenance)) + 
  geom_bar() + 
  labs(title = "Bar plot of type and provenance", x = "Blade Shape categories")
```

```{r}

# 20241129 ######

source("plots/source/plotting_functions.R")

plot_name <- "C:/Users/jhunke/Documents/session3_dartpoints_ggplot3.png"



#png(plot_name, width = 700, height = 300)


three_histograms(variable_1 = stone_tools_data$thickness,
                 variable_2 = stone_tools_data$breadth,
                 variable_3 = stone_tools_data$thickness,
                 variable_1_main = "fsfdsfd",
                 variable_2_main = "fgdfdsagfsg",
                 variable_3_main = "gdfgfds",
                 variable_1_xlab = "variableAA 1",
                 variable_2_xlab = "variableAAA 2",
                 variable_3_xlab = "variableAAA 3"
                 )


knitr::include_graphics(plot_name)
#dev.off()
```

# Überschrift 1. Grades

## Überschrift 2. Grades

###### Überschrift 6. Grades

| Spalte 1 | Spalte 2 |
|:---------|:--------:|
| Zeile 1  | Zeile 2  |

Text mit Fußnote[\^fußnote] Mein beliebiger Text [\^fußnote]: Mein Fußnotentext

```{r}
#png("plots/session3_dartpoint_ggplot2.png")
#svg("plots/session3_dartpoints_ggplot2.svg")
svg("C:/Users/jhunke/Documents/session3_dartpoints_ggplot2.svg")
ggplot(stone_tools_data, aes(x = breadth, y = blength, colour="green", shape=inventory_number),colour="green") +
```

```{r}
```

```{r}
```

```{r}
```

```{r}
geom_point(colour = "red", shape = 24) +
  labs(title = "Length vs Width by Blade Shape 03")
#, 
#                       colour = "AAAAred", # use factor as it is, ggplot() will convert it into colours
#                       shape = 23)) + # use factor as it is, ggplot() will convert it into shapes

dev.off()

```

#fdsfdsfds

```{r}

plot_name <- "C:/Users/jhunke/Documents/session3_dartpoints_ggplot2.png"

stone_tools_data_table_type_and_provenance <- table(stone_tools_data_table_type_and_provenance)



knitr::include_graphics(plot_name)

```
